---
title: "Refuge Survey Activities, Alaska" 
date: "`r format(Sys.Date(), '%B %Y')`"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
    self_contained: yes
    highlight: pygments
---


```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(odbc)
library(DT)
library(tidyselect)
  
knitr::opts_chunk$set(echo = TRUE)

source("../../R/query_iris.R")
read_chunk("../../R/plots.R")
read_chunk("../../R/summaries.R")
```

```{r get_data, echo=FALSE}

survey_data <- query_iris("Refuges", "DimSurvey") %>%
  filter(Station %like% "FF07%") %>%
  filter(SurveyStatus != "Historic") %>%
  collect()

# dim_annual_activity <- query_iris("Refuges", "DimSurveyAnnualActivity")
# dim_annual_activity_ak <- dim_annual_activity %>%
#   filter(Station %like% "FF07") %>%
#   collect()


```


# Introduction

Here is where we would have text with inline code for dynamic summary stats. For example, there are currently `r length(survey_data$surveyId)` PRIMR records for the Alaska region. The earliest survey started in `r min(survey_data$startYear)`. The longest running historical survey ran `r max(as.numeric(survey_data$endYear, na.rm=T) - as.numeric(survey_data$startYear, na.rm=T), na.rm=T)` years.

```{r figure1, fig.cap="Number of current surveys by Refuge, Alaska Region.", echo=FALSE}
```


# Tables

```{r table1, echo=FALSE, message=FALSE}
```

# Appendix

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
