---
title: "Refuge Survey Activities, Alaska" 
date: "`r format(Sys.Date(), '%B %Y')`"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
    self_contained: yes
    highlight: pygments
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r get_data, echo=FALSE}

survey_data <- query_iris("Refuges", "DimSurvey") %>%
  filter(Station %like% "FF07%") %>%
  filter(SurveyStatus != "Historic") %>%
  collect()
```


# Introduction

Here is where we would have text with inline code for dynamic summary stats. For example, there are currently `r length(survey_data$surveyId)` PRIMR records for the Alaska region. The earliest survey started in `r min(survey_data$startYear)`. The longest running historical survey ran `r max(as.numeric(survey_data$endYear, na.rm=T) - as.numeric(survey_data$startYear, na.rm=T), na.rm=T)` years.

```{r figure1, fig.cap="Number of current surveys by Refuge, Alaska Region.", echo=FALSE}
survey_data %>%
  mutate(stationName = fct_reorder(stationName, id, .fun = 'length')) %>%  # Order refuges by number of surveys
  ggplot(aes(stationName, fill = status.name)) +
  geom_bar() +  #bar plot
  coord_flip() +  # flip the axises
  theme(axis.title.y = element_blank(),
        legend.position = c(0.85, 0.2)) +  # Remove to x axis label
  labs(y = "Number of current surveys",
       fill = "Survey status") # custom y axis label
```


# Tables

```{r table1, echo=FALSE, message=FALSE}
foo <- survey_data %>%
  select(stationName, type.name, id) %>%
  group_by(stationName, type.name) %>%
  summarise(count = length(id)) %>%
  spread(type.name, count)

datatable(foo)

survey_data %>%
  select(stationName, type.name, id) %>%
  group_by(stationName, type.name) %>%
  summarise(count = length(id)) %>%
  spread(type.name, count) %>%
  DT::datatable()
```

# Appendix

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```
